|

### 2024-01-22 rmds/figures-supp.Rmd
updates

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - free", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = "Interval coverage - Length at 50% maternity") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6.
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - free"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S7. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - free", par_name %in% "c")) %>% 
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_maternal)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_maternal, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. maternal")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S8. Median number of females in maternal condition in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - free", par_name %in% "c")) %>% 
ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_immature)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_immature, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. immature")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S9. Median number of immature females in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage

>>>>

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = "Interval coverage - Length at 50% maternity") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6.
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - estimated"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S7. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_maternal)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_maternal, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. maternal")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S8. Median number of females in maternal condition in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage

```{r, fig.width = 11, fig.height = 8.5}
filter(data, method_long %in% c("3PLF - estimated", par_name %in% "c")) %>% 
ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = n_immature)) + 
  geom_text(aes(x = as.factor(Nsamples_sel), y = repro_freq, label = round(n_immature, 0))) +
  scale_fill_viridis_c(trans = "log10") + 
  guides(fill = guide_colorbar(title = bquote(atop("Median", "n. immature")))) + 
  facet_wrap(~species, nrow = 2) +
  theme_half_open() + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure S9. Median number of immature females in simulated data that were used to estimate maternity parameters subject to varying sample size, gear selectivity, reproductive frequency. 250 iterations were carried out for each simulation. 
\newpage
